---
title: "Relationship between Age and the party people support "
author: "Boyu Sheng"
date: 2020-07-23T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
#install.packages("tidyverse")
#install.packages("devtools")
#devtools::install_github("hodgettsp/cesR")
#install.packages("skimr")
library(tidyverse)
library(visdat)
library(cesR)
library(skimr)
```
#Abstract

This piece of work uses the rmarkdown as a tool to develop the variables and observers in the 2019 Canadian General Election


#Introduction

In the 2019 election, the survey showed that there is a outstanding support for the Conservative party yet the Conservatives still lost the election and obtained less seats in the parliament. Among those group people, I mainly focus the variable of year of birth and the federal party that they support. 

In the graph, one thing that we can conclude is that the survey focused more on the people who are 40 years old or more and the statistics itself is biased.

After the graph, there will be a general diccussion and the weakness that we encountered in this survey. 


```{r download, warning=FALSE, message=FALSE}

#install.packages("devtools")
#devtools::install_github("hodgettsp/cesR")

cesR::get_ces("ces2019_web")
glimpse(ces2019_web)
```


```{r}
head(ces2019_web)
```

```{r}

ces2019_web <-
  ces2019_web %>%
  select(cps19_yob, pid_en)

ces2019_web <-
  ces2019_web %>%
  filter(cps19_yob > 20)



#visdat::vis_dat(ces2019_web)

#skimr::skim(ces2019_web)

#class(ces2019_web$ces_code)



```

```{r}
ces2019_web <-
  ces2019_web %>%
  filter(! is.na(pid_en))
```

```{r}

ces2019_web %>%
  ggplot(aes(x = pid_en)) + 
  geom_bar()

```


```{r}

ces2019_web %>%
  ggplot(aes(x = cps19_yob)) +
  geom_histogram(fill = "pink", color = "green") +
  labs(x = "yob",
       y = "number",
       title = "Distribution of year of birth in 2019 CES") +
  theme_bw()
```

# Discussion

The sample mainly collected 37230 respondents in the survey and most of the people were born in the time period of 1930s-1970s and the outcome shows that they are most likely to consider themselves as Conservative. Liberal is the only competitive rival in the election. And the share of Green Party, NDP, Bloc and People's Party control relative small portions of polls in the election. 



# Weakness

This sample only shows 37230 respondents and it is a relatively small amount compared to the whole population of 30 millions in Canada. Moreover, the sample neglected the people who were born after 1980s who can lead to a significant change in the result of the election. In fact, the Liberal Party has won the election possibly due to the number of the young voters. 


#References
Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686,
  https://doi.org/10.21105/joss.01686
Keller, Sally A., Stephanie S. Shipp, Aaron D. Schroeder, and Gizem Korkmaz, 2020, ‘Doing Data Science: A Framework and Case Study’ Harvard Data Science Review, 2 (1), https://doi.org/10.1162/99608f92.2d83f7f5 (Links to an external site.). 
Nelder, John A., 1999, ‘From Statistics to Statistical Science’, Journal of the Royal Statistical Society, Series D (The Statistician), 48 (2), pp. 257-269.
Reid, Nancy, 1994, ‘A Conversation with Sir David Cox’, Statistical Science, 9 (3), pp. 439-455. doi:10.1214/ss/1177010394, https://projecteuclid.org/euclid.ss/1177010394 (Links to an external site.).
Hadley Wickham, Jim Hester and Winston Chang (2020). devtools: Tools to Make Developing R Packages Easier.
  https://devtools.r-lib.org/, https://github.com/r-lib/devtools.
 JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and
  Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents
  for R. R package version 2.3. URL https://rmarkdown.rstudio.com.

  Yihui Xie and J.J. Allaire and Garrett Grolemund (2018). R Markdown: The Definitive Guide. Chapman and
  Hall/CRC. ISBN 9781138359338. URL https://bookdown.org/yihui/rmarkdown.
Paul A. Hodgetts and Rohan Alexander (2020). cesR: Access the CES Datasets a Little Easier.. R package
  version 0.1.0.












  







